\mytitle

### 2015-07-28 diss_valid_vs_time.tex
Minor changes
Changes in caption

\caption{Changes in mixing ratios of $O_3$, $O(^1D)$, $OH$, $NO$, $NO_2$, $HO_2$, $H_2O_2$, total $RO_2$ and $CO$ with time (in ppb) under different $NO_x$ and $VOC$ conditions: 
$NO_x=50$ ppt and minimum sum of $VOCs$ (blue solid lines), 
$NO_x=50$ ppt and maximum sum of $VOCs$ (red solid lines), 
$NO_x=5$ ppb and minimum sum of $VOCs$ (blue dashed lines),
$NO_x=5$ ppb and maximum sum of $VOCs$ (red dashed lines), Minimum sum of $VOCs$ corresponds to case A in Table 5, maximum sum of $VOCs$ - case K. Simulation time 24 hours.}
\label{fig:res0}
\end{figure}

>>>>

\caption{Changes in mixing ratios of $O_3$, $O(^1D)$, $OH$, $NO$, $NO_2$, $HO_2$, $H_2O_2$, total $RO_2$ and $CO$ with time (in ppb) under different $NO_x$ and $VOC$ conditions with alkyl nitrate chemistry switched off: 
$NO_x=50$ ppt and minimum sum of $VOCs$ (blue solid lines), 
$NO_x=50$ ppt and maximum sum of $VOCs$ (red solid lines), 
$NO_x=5$ ppb and minimum sum of $VOCs$ (blue dashed lines),
$NO_x=5$ ppb and maximum sum of $VOCs$ (red dashed lines), Minimum sum of $VOCs$ corresponds to case A in Table 5, maximum sum of $VOCs$ - case K. Simulation time 24 hours.}
\label{fig:model_validation}
\end{figure}
